Switch equivalence and weak prime domains for fusions

### 2024-05-30 fusione.tex
minori

@@

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}

@@

\begin{remark}\label{rem:pb}
	Let $X$ be an object of $\X$, with $\X$ $\mathcal{M}$-adhesive. We can consider  the full subcategory $\mathcal{M}/X$ of $\X/X$ made by arrows in $\mathcal{M}$. Since $\X$ has all $\mathcal{M}$-pullbacks, for every arrow $f\colon X\to Y$ we have a functor $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X $ sending $m\colon \mto X$ to a chosen pullback of it along $f$.
	\end{remark}

@@

\iffalse 
\begin{definition} \index{source} \index{sink} \index{pushout!wide -} \index{pullback!wide -}
	Given a set $I$, a  \emph{source}  (\emph{sink}) is a family $\{f_i\}_{i\in I}$ of arrows  $f_i\colon X\to Y_i$ ($f_i\colon Y_i\to X$) with the same (co)domain. A $\emph{wide pushout}$ (pullback) is the colimit (limit) of a source (sink). We will use $c_i$ ($p_i$) to denote the coprojection from $Y_i$ (the projection to $Y_i$) and $c_X$ to denote the one from $X$.
\end{definition}

@@

		\item By \cref{rem:copro} and point three of \cref{cor:iso} it is enough to show that $c_X$ is in $\mathcal{E}$. Since $(\mathcal{E}, \mathcal{M})$ is a factorization system then $c_X=m\circ e$ for some $m\colon E\to C$ in $\mathcal{M}$ and $e\colon X\to E$ in $\mathcal{E}$ to get, from \cref{rem:copro}, a square
		\[\xymatrix{X\ar[r]^{e} \ar[d]_{e_i} & V \ar[d]^{m} \\ Y_i \ar@{.>}^{k_i}[ur] \ar[r]_{c_i}  & Z}\]
		and the left lifting property provides, for every $i\in I$, the dotted arrow $k_i\colon Y_i\to e$. Let $k$ be the the induced arrow $Z\to V$. Then
		\begin{align*}
			m\circ k\circ c_i&=m\circ k_i\\&=c_i
		\end{align*}
		hence $m\circ k=\id{Z}$. By \cref{cor:iso} $m\in \mathcal{M}$ thus it is an isomorphism and we can conclude. \qedhere 
	\end{enumerate}
\end{proof}
\fi

\begin{definition}
	contenuto...
\end{definition}
\begin{proposition}
	inf
\end{proposition}
\begin{proof}
\end{proof}
Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem to the partial ordered case.

@@

@@

\iffalse 
\begin{remark}
	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle below:
	\[\xymatrix{M\ar[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
	Notice that, if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.  
\end{remark}
\fi

>>>>

\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}

\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}

@@

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\E{\textbf {\textup{E}}}

@@

\begin{remark}\label{rem:pb}
	Let $X$ be an object of $\X$, with $\X$ an $\mathcal{M}$-adhesive. category We can consider  the full subcategory $\mathcal{M}/X$ of $\X/X$ made by arrows in $\mathcal{M}$. Since $\X$ has all $\mathcal{M}$-pullbacks, for every arrow $f\colon X\to Y$ we have a functor $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X $ sending $m\colon M \mto X$ to a chosen pullback of it along $f$.
	\end{remark}

@@

\begin{definition} 
	Given a set $I$, a  \emph{source}  (\emph{sink}) is a family $\{f_i\}_{i\in I}$ of arrows  $f_i\colon X\to Y_i$ ($f_i\colon Y_i\to X$) with the same (co)domain. A $\emph{wide pushout}$ (pullback) is the colimit (limit) of a source (sink). We will use $c_i$ ($p_i$) to denote the coprojection from $Y_i$ (the projection to $Y_i$) and $c_X$ to denote the one from $X$.
\end{definition}

@@

		\item By \cref{rem:copro} and point three of \cref{cor:iso} it is enough to show that $c_X$ is in $\mathcal{E}$. Since $(\mathcal{E}, \mathcal{M})$ is a factorization system then $c_X=m\circ e$ for some $m\colon E\to C$ in $\mathcal{M}$ and $e\colon X\to E$ in $\mathcal{E}$ to get, from \cref{rem:copro}, a square
		\[\xymatrix{X\ar[r]^{e} \ar[d]_{e_i} & V \ar[d]^{m} \\ Y_i \ar@{.>}^{k_i}[ur] \ar[r]_{c_i}  & Z}\]
		and the left lifting property provides, for every $i\in I$, the dotted arrow $k_i\colon Y_i\to e$. Let $k$ be the the induced arrow $Z\to V$. Then
		\begin{align*}
			m\circ k\circ c_i&=m\circ k_i\\&=c_i
		\end{align*}
		hence $m\circ k=\id{Z}$. By \cref{cor:iso} $m\in \mathcal{M}$ thus it is an isomorphism and we can conclude. \qedhere 
	\end{enumerate}
\end{proof}

Let $\mathcal{M}$ be a class of monos in a category $\X$, then $\mathcal{M}/X(f,g)$ has cardinality at most one for every two arrows $f$ and $g$ with codomain $X$. Thus it is a preordered class, in which $f\leq g$ if and only if  $\mathcal{M}/X(f,g)$ is non-empty. Now, it is immediate to notice that $f\leq g$ and $g\leq f$, then there exists a (unique) isomorphism fitting in the triangle below.
\[\xymatrix{A\ar@{.>}[rr]^{\phi} \ar[dr]_{f} && B \ar[dl]^{g}\\ & X}\]
In such a case we will write $f\equiv g$. It is immediate to see that in this way we get an equivalence relation on the class of objects of $\mathcal{M}/X$.

\begin{definition} Let $\mathcal{M}$ be a class of monos in a category $\X$. For every object $X$ a \emph{$\mathcal{M}$-subobject} is an equivalence class $[f]$ of an object $f$ in $\mathcal{M}/X$ with respect to $\equiv$. Given two \emph{$\mathcal{M}$-subobjects} $[f]$ and $[g]$, represented by $f$ and $g$, respectively, we will define $[f]\leq [g]$ if and only if $f\leq g$. It is immediate to see that this defines a partially ordered class $(\sub{M}{X}{X}, \leq)$.

	When $\mathcal{M}$ coincides with the class of all monos we will suppress the prefix, so that a \emph{subobject} is just an equivalence class of a mono and $((\msub{X}{X}), \leq)$ will denote the ordered class of such subobjects of $X$.
\end{definition}
\begin{remark}\label{rem:size}
	Every $\mathcal{M}$-adhesive cateory $\X$ admits a full and faithful functor $F:\X\to \E$ into a topos $\E$, sending arrows in $\mathcal{M}$ to monomorphisms \cite{castelnovo2023thesis}. Since every topos is \emph{well-powered}, i.e. $\msub{E}{E}$ is a set for every object $E$ \cite{maclane2012sheaves}, we can deduce  that, for every $X$ in $\X$, $\sub{M}{X}{X}$ is actually a set too.
\end{remark}

\begin{remark}
	contenuto...
\end{remark}

Our next step is to compute infima in $(\sub{M}{X}{X}, \leq)$.

\begin{proposition}
	inf
\end{proposition}
\begin{proof}
\end{proof}
\begin{corollary}
	contenuto...
\end{corollary}

Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem to the partial ordered case.

@@

\begin{proposition}\label{cor:pbpres}
	Let $\mathcal{M}$ be a class of monos in a category $\X$ stable under pullbacks.  Let $f\colon X\to Y$ be an arrow admitting a pullback along any arrow $m\colon M\to Y$. Then the pullback functor $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X$ preserves all limits.
\end{proposition}
\begin{proof}
Let $()$

@@

\begin{example}
	>complete
\end{example}

\begin{example}
	>finit
\end{example}
